Cooperative Kernels: GPU Multitasking for Blocking Algorithms

### 2017-06-29 write-ups/FSE/paper.tex
Started working on camera-ready.

@@

@@

The mutexes and barriers used by these two examples appear to run
reliably on current GPUs for kernels that are executed with no more
workgroups than there are compute units.  This is due to the fairness
of the occupancy-bound execution model that current GPUs have been
shown, experimentally, to provide.  But, as discussed in
\mysec\ref{sec:intro}, this model is not endorsed
language standards or vendor implementations, and is unlikely to be respected in the future.
%
In \mysec\ref{sec:programmingguidelines} we show how the work stealing
and graph traversal examples of \myfigs\ref{fig:workstealing} and~\ref{fig:graphsearch} can be
updated to use our cooperative kernels programming model to resolve
the scheduling issue.

>>>>

\ADComment{Reviewer comment: Given that the authors propose that the OpenCL (and other frameworks) be modified to incorporate their non-cooperative kernel implementation, they should explain why GPU vendors would prefer to adopt the authors' approach over a more functional preemptive multitasking one.  Are particular properties of GPU hardware or software stack (e.g. size of context) hindering the use of preemptive multitasking?  How is the effect of these properties minimized under the authors' proposed approach?}

\ADComment{Get something in on NVIDIA's recent developments.}

\ADComment{Possibly cite: Marc Tarpenning. Cooperative Multitasking in C++. Dr. Dobb's Journal, April 01, 1991}

\ADComment{Please outline the rationale behind your choice of the particular primitives you propose.}

@@

\ADComment{Reviewer comment: Section 2.2 would benefit from a short introduction explaining how the proposed examples fail in current implementations.}

@@

The mutexes and barriers used by these two examples appear to run
reliably on current GPUs for kernels that are executed with no more
workgroups than there are compute units.  This is due to the fairness
of the occupancy-bound execution model that current GPUs have been
shown, experimentally, to provide.  But, as discussed in
\mysec\ref{sec:intro}, this model is not endorsed
by language standards or vendor implementations, and is unlikely to be respected in the future.
%
In \mysec\ref{sec:programmingguidelines} we show how the work stealing
and graph traversal examples of \myfigs\ref{fig:workstealing} and~\ref{fig:graphsearch} can be
updated to use our cooperative kernels programming model to resolve
the scheduling issue.
